PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-27 paper.tex
Update on Overleaf.

\begin{itemize}
\item
  Condition A: one pair of children freely play together on the
  sandtray.
\item
  Condition B: one child play together with the robot, the robot does
  not exhibit any social behaviour.
\end{itemize}

@@

\begin{itemize}
\item
  Condition A: 40 pairs of children (ie, 80 children)
\item
  Condition B: 40 children
\end{itemize}

@@

Normally developping children, from local primary schools and nurseries.

@@

On large touchscreen, mounted on a horizontal frame (\emph{sandtray});
both children (condition A, Figure 2) or the child and the robot
(condition B, Figure 3) are facing each other.

@@

The experimenter stays in the room, visible from the child. When
requested by the nursery or school, another childminder (nursery/school
staff) can be present in the room. She/he is however asked not to step
in during the experiment.

The interaction is recorded by 3 cameras (on `environment' camera
filming the whole scene; two RGB-D cameras, focused on each of the
children faces).

Audio is recorded as well with 2 microphones integrated to the RGB-D
cameras.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  welcome (5 min):

  \begin{itemize}
  \item
    place children on cushions
  \item
    give them the yellow/purple sport bibs
  \item
    make sure hairs are tied (to help with face tracking)
  \item
    ask names (but do not write them down)
  \item
    fill up questionaire on the tablet -- age, gender, familiarity with
    tablet
  \item
    \textbf{remind the children that they can withdraw at anytime}
  \item
    \textbf{explain the purpose of the study: showing robots how
    children play}
  \item
    in condition B, present briefly the robot -- saying it is not a very
    sociable robot, and it might play alone.
  \end{itemize}
\item
  visual focus task (30 seconds)
\item
  tutorial (1-2 min): explain how to interact with the game, ensure the
  children are confident with the manipulation/drawing
\item
  main freeplay task (up to 40 min):

>>>>

\begin{itemize}
\item
  Condition A: one pair of children play freely  simultaneously on the
  sandtray.
\item
  Condition B: one child plays on the sandtray with the robot. The robot does
  not exhibit any social behaviour.
\end{itemize}

@@

\begin{itemize}
\item
  Condition A: 40 pairs of children (i.e., 80 children)
\item
  Condition B: 40 children
\end{itemize}

@@

Normally developing children, from local primary schools and nurseries.

@@

On large touchscreen, mounted on a horizontal frame (\emph{sandtray});
both children (Condition A, Figure 5 left) or the child and the robot
(Condition B, Figure 5 right) are facing each other.

@@

The experimenter stays in the room, visible to the child. When
requested by the nursery or school, another childminder (nursery/school
staff) can be present in the room. She/he is however asked not to step
in during the experiment.

The interaction is recorded by 3 cameras: one `environment' camera
filming the whole scene and two RGB-D cameras, one focused on each of the
children's faces. Audio is recorded using the microphones integrated to the RGB-D cameras.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Welcome (5 min):

  \begin{itemize}
  \item
    \textbf{explain the purpose of the study: showing robots how
    children play}
    \item
    in condition B, present briefly the robot -- saying it is not a very
    sociable robot, and it might play alone.
  \item
    place children on cushions
  \item
    give them the yellow/purple sport bibs
  \item
    make sure their hair is tied back (to help with face tracking)
  \item
    ask names (but do not write them down)
  \item
     complete questionnaire on the tablet -- age, gender, familiarity with
    tablet
  \item
    \textbf{remind the children that they can withdraw at anytime}

  \end{itemize}
\item
  visual focus task (30 seconds)
\item
  tutorial (1-2 min): explain how to interact with the game, ensure the
  children are confident with the manipulation/drawing
\item
  main freeplay task (up to 40 min):
